### 2018-02-27 Maths Notes/Statistics/S3/Estimation/Estimation.tex
S3 Notes Update

>>>>

\subsubsection{Example}
\textit{The weight of boys and girls in a certain school are known to be normally distributed with standard deviations of 5kg and 8kg respectively. A random sample of 25 boys had a mean weight of 48kg and a random sample of 30 girls had a mean weight of 45kg.\\
Stating your hypothesis clearly test, at the 5\% level of significance, whether or not there is evidence that the mean weight of boys in the school is greater than the mean weight of girls.}\\
Write down the two distributions
$$\overline{X_B}\sim N\Big(\mu_B,\frac{5^2}{25}\Big) \qquad \qquad \overline{X_G}\sim N\Big(\mu_G,\frac{8^2}{30}\Big)$$
State the two hypotheses
$$H_0: \ \mu_B=\mu_G$$
$$H_1: \ \mu_B>\mu_G$$
Find the $z$ value
$$z=\frac{48-45-(0)}{\sqrt{\frac{5^2}{25}+\frac{8^2}{30}}}=1.6947$$
Find the critical value from the percentage points table
$$C.V.=1.6449$$
Compare the critical value to the z value
$$1.6449<1.6947$$
Write conclusion
As z is not in the critical region there is not enough evidence to reject $H_0$, there is not enough evidence to suggest that the mean weight of boys is greater than the mean weight of girls.
